### 2012-03-30 paper.tex
Updated BibTeX keys

\frenchspacing \title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Michael McCracken, Seth Pruitt, Ross
    Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010 Joint
    Statistical Meetings, and in many seminars at \textsc{ucsd}, and
    espeically Graham Elliott for their valuable suggestions, feedback
    and advice in writing this paper.  I would also like to thank Amit
    Goyal for providing computer code and data for his 2008 RFS paper
    with Ivo Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State
  University, Economics Department}
\date{October 24, 2011}

@@

Although \oos\ comparisons have been popular in macroeconomics and
finance since \citepos{meese_empirical_1983} seminal study of exchange
rate models, it is unclear from a theoretical perspective whether or
not the statistics are useful.  Empirical researchers often cite
``overfit'' or ``instability'' as reasons for using \oos\ comparisons,
as in \citet{stock_forecasting_2003}, but neither term is precisely
defined or formalized.  Compounding this problem, the asymptotic
distributions of these statistics are derived under conditions that
rule out either instability or overfit and allow a researcher to use a
conventional in-sample comparison---a variation of the F-test, for
example.  As \citet{inoue_kilian_2004} argue, the statistics
themselves are designed to test hypotheses that can be tested by these
in-sample statistics.  For example, \citet{diebold_comparing_1995} and
\citet{west_asymptotic_1996} derive the limiting distributions of many
popular \oos\ test statistics under conditions that would justify
these full-sample tests.\footnote{In this paper, we will refer to
  their basic \oos\ $t$-test as the \dmw\ test.}  Much of the
subsequent research by \citet{chao_out_2001},
\citet{clark_tests_2001,clark_evaluating_2005},
\citet{corradi_consistent_2002,corradi_recent_2004},
\citet{clark_using_2006,clark_approximately_2007},
\citet{mccracken_asymptotics_2007}, \citet{anatolyev_inference_2008},
and others relaxes several of Diebold and Mariano's and West's
assumptions, but maintains the stationarity and dependence conditions
that permit in-sample comparisons.\footnote{Like us,
  \citet{anatolyev_inference_2008} allows the number of regressors to
  increase with $T$.  But in that paper, they increase slowly enough
  that the \ols\ coefficients are consistent and asymptotically
  normal.}  \citet{giacomini_tests_2006}, and
\citet{giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
are exceptions.  Instead of focusing on hypotheses that can be tested
by in-sample comparisons, \citet{giacomini_tests_2006} derive an \oos\
test for the null hypothesis that the difference between two models'
\oos\ forecasting performance is unpredictable, a martingale
difference sequence, \citet{giacomini-rossi-2009-REStud} test whether
the \oos\ forecasting performance of a model suffers from a breakdown
relative to its in-sample performance, and
\citet{giacomini-rossi-2010-JAppliedEconometrics} test whether the
forecasting performance is stable. However, those papers focus on a
particular \oos\ estimation strategy and do not address why naive
\oos\ comparisons might be generally useful.

Since in-sample and \oos\ statistics require similar assumptions and
test similar hypotheses, one might expect that they would give similar
results.  They do not.  Generally in-sample analysis supports more
complicated theoretical models and \oos\ analysis supports simple
benchmarks, as seen in \citet{meese_empirical_1983},
\citet{stock_forecasting_2003}, and \citet{goyal-welch-2008-rfs}.
Since these different approaches strongly influence the outcome of
research, it is important to know when each is appropriate.  The
explanations in favor of \oos\ comparisons claim that they should be
more robust to unmodeled instability
\citep{clark_power_2005,giacomini_tests_2006,giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
or to overfit \citep{mccracken_data_1998,clark_can_2004}.  Both
explanations presume that the in-sample comparison is invalid and the
\oos\ comparisons are more reliable.  Of course, as
\citet{inoue_kilian_2004,inoue_selection_2006} point out, both
in-sample and \oos\ methods could be valid, but the \oos\ methods
could have lower power.

In this paper, we study the ``overfit'' possibility and leave
``instability'' to future research. This paper uses dimension
asymptotics to study the behavior of \oos\ comparisons when at least
one of the models is overfit---when the number of its regressors
increases with the number of observations so that their ratio remains
positive.  We focus on linear regression models estimated with a fixed
training window, but our basic conclusions should be true for other
estimation strategies and models as well.  Under this asymptotic
theory, the \ols\ coefficient estimator is no longer consistent or
asymptotically normal \citep{huber_robust_1973} with positive variance
in the limit.  Even so, we show that the usual \oos\ average is
asymptotically normal and can consistently estimate the difference
between the models' expected loss in periods $T+1,T+2,\dots$
conditional on the on the data available in period $T$, a time-series
analogue to the generalization error.\footnote{See, for example,
  \citet{elemstatlearning}.}  Under these asymptotics, the
generalization error does not converge to the expected performance of
the pseudo-true models, so the in-sample and \oos\ comparisons measure
different quantities and should be expected to give different results
for reasons beyond simple size and power comparisons.  Under our
theory, the model that is closer to the true \dgp\ in population can
forecast worse.  In such a situation, an in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an \oos\ comparison would correctly fail to reject the null that the
benchmark is more accurate.\footnote{In a pair of papers similar to
  ours, \citet{RePEc:fip:fedkrw:rwp09-10,RePEc:fip:fedkrw:rwp09-11}
  study in-sample and \oos\ tests that the larger model has nonzero
  coefficients that are too close to zero to expect the model to
  forecast more accurately.  Like this paper, they argue that the
  larger model can be true but less accurate.  However, they focus on
  an aspect of the \dgp\ that makes this phenomenon likely, while we
  focus on the coefficient estimates that produce less accurate
  forecasts.}

This result justifies \oos\ comparisons when researchers want to
choose a model for forecasting.  Although there has been little
emphasis on hypothesis testing in these settings, testing is usually
appropriate: there is usually a familiar benchmark model in place, and
the cost of incorrectly abandoning the benchmark for a less accurate
alternative model is higher than the cost of incorrectly failing to
switch to a more accurate alternative.\footnote{These costs can be
  monetary, in the form of computer upgrades, software installation,
  and training, or they can be reputational costs.}
We show that the \dmw\ test lets the forecaster control the
probability of the first error, just as with conventional hypothesis
testing.

@@

Since the \ols\ coefficient estimator is no longer consistent or
asymptotically normal, the F-test and Wald tests are no longer
asymptotically valid.  Moreover,
\citet{efron_biased_1986,efron_estimation_2004} shows that naive
comparisons of in-sample loss overestimate models' accuracy by a
factor proportional to $K/T$, $K$ being the number of regressors.  But
modifications of the F-test are valid under this asymptotic theory, as
shown by \citet{boos_anova_1995}, \citet{akritas_asymptotics_2000},
\citet{akritas_heteroscedastic_2004}, and
\citet{calhoun_hypothesis_2009}, among others.  Such results establish
that hypotheses about the parameters of the \dgp\ can be tested
in-sample even if one or both models are overfit.  For that very
reason, these tests can not reliably choose a model for forecasting
and will reject the benchmark too often.  We show this analytically in
Section~\ref{sec:insample}.  Moreover, under this asymptotic theory,
many recent \oos\ test statistics, such as those derived by
\cite{clark_tests_2001,clark_evaluating_2005},
\citet{mccracken_asymptotics_2007}, and
\citet{clark_using_2006,clark_approximately_2007} should behave like
the F-test.  These tests are also designed to reject the benchmark
when the alternative model is true, and so they may reject too often
when the benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
\infty$ (with the number of regressors fixed), these statistics behave
like the \dmw\ test when $P$ is small, but should over-reject the
benchmark when $P$ is large.  Section~\ref{sec:mc} presents
simulations that support these claims.

@@

The first assumption is a standard condition on the dependence of the
underlying stochastic array.  We assume that the array is absolutely
regular instead of strong mixing, which is more common in
econometrics, because absolute regularity admits a particular coupling
argument \citep{berbee_random_1979} that is unavailable for strong
mixing sequences.  Please see, for example,
\citet{davidson_stochastic_1994} for a discussion of these mixing
conditions.

@@

The next assumption restricts the class of variance estimators we will
consider.  We use the same class of estimators studied by
\citet{de_jong_consistency_2000} (their class $\mathcal{K}$); see
their paper for further discussion.

@@

Both sets of simulations support our theoretical results.  The first
simulation confirms that the \dmw\ \oos\ $t$-test is centered at $E_R
\bar D_1$ for all choices of $P$ and $R$ and is centered on $E_T \bar
D_2$ only when $P$ is small.  The second simulation confirms that the
\dmw\ test has correct size for the null hypothesis that $E_T \bar D_2
\leq 0$ when $P$ is small and that tests designed to test whether the
benchmark is true, like the F-test and Clark and West's (2006, 2007)
and McCracken's (2007) \oos\ tests can reject by much more than their
nominal size when testing the null $E_T \bar D_2 \leq 0$.
Moreover, these simulations demonstrate that the restriction $P^2/T
\to 0$ is binding in practice, as the \dmw\ test under-rejects and has
very low power when it is not satisfied.
\section{Empirical Exercise}\label{sec:empirics}
This section presents an analysis of equity premium predictability
similar to \citet{goyal-welch-2008-rfs}.\footnote{All of the
  calculations in this section are done in R \citep{rproject}.  We
  also use code provided by \citet{zeileis-hothorn-2002-RNews},
  \citet{zeileis-2004-JStatSoftware}, and \citet{harrell-2010-R}.}  We
estimate the expected forecasting performance of the largest model
they consider, a model with 13 regressors, using 81 observations
(annual data from 1928 to 2009).  We construct confidence intervals
for the difference in performance between this model and a prevailing
mean benchmark, and do so for different values of $R$ and $P$ to
examine the effect of the training and test sample choice on this
\oos\ statistic.  We find that the estimate of the larger model's
\mse\ decreases relative to the benchmark as $R$ increases, but it is
never smaller than the benchmark's.  This result, combined with the
larger model's in-sample significance, suggests that there may be a
real relationship between the equity premium and some of these
predictors, but that the relationship can not be estimated accurately
enough to be useful for forecasting and supports
\citepos{goyal-welch-2008-rfs} conclusions.  These results hold even
when imposing \citepos{campbell-thompson-2008-rfs} restriction that
the equity premium forecast be non-negative.

We'll start with a very brief review.  \citet{goyal-welch-2008-rfs}
study the \oos\ forecasting performance of different variables thought
to predict the equity premium (calculated as the difference between
the return on the S\&P 500 index and the T-bill rate).  Some of these
variables are listed in
Table~\ref{tab:equity}.\footnote{Table~\ref{tab:equity} only lists the
  variables used in \citepos{goyal-welch-2008-rfs} ``kitchen sink''
  model.  Some of the variables that they use in bivariate models are
  excluded from this model either because the series are too short or
  because the variables are linear combinations of other variables.}
\citet{goyal-welch-2008-rfs} estimate the \oos\ forecasting
performance of bivariate models of the form
\[
r_{t+1} = \beta_0 + \beta_1 x_t + \varepsilon_{t+1}
\]
using \ols\ with a recursive window, where $r_{t+1}$ is the equity
premium and $x_t$ is a generic predictor, as well as some larger
models.  They find that these models forecast no better than the
prevailing mean of the equity premium.
\citet{campbell-thompson-2008-rfs} find that nonlinear extensions of
Goyal and Welch's models are more accurate, either imposing sign
restrictions on the estimated coefficients or imposing that the
forecast be non-negative, but do not test for significance.

Obviously, \citepos{goyal-welch-2008-rfs} bivariate models do not
match the asymptotic theory of this paper, so we restrict our
attention here to their ``kitchen sink'' model, which includes all of
the variables, except for a few dropped because of data availability or
(perfect) multicollinearity.  Formally, the benchmark and alternative models are
\begin{eqnarray}
  \label{eq:3}
  r_{t+1} &=& \mu + \varepsilon_{1,t+1} \\
  \label{eq:2}
r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \varepsilon_{2,t+1}  
\end{eqnarray}
respectively and are estimated by \ols\ using the fixed-window scheme.
The predictors are listed in Table~\ref{tab:equity}; for a detailed
description of each predictor, please see Goyal and Welch's original
paper.  In this model, there are 13 regressors (including the constant
term) and we estimate the coefficients using annual data from 1928 to
2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
present results for one of \citepos{campbell-thompson-2008-rfs}
restricted forecasting models.  For this model, we estimate
\eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
non-negative for each forecast.  We then calculate the \oos\ test just
as for the unconstrained model.

Table~\ref{tab:gwinsample} gives the results of the full sample
regression for Equation~\eqref{eq:2}, using Newey-West standard errors
with two lags \citep{newey_simple_1987}.\footnote{We compare the test
  statistic to critical values from the $F$-distribution.}  The
$p$-value is very small (less than 0.01), indicating that the
coefficients are nonzero in population and at least one of these
predictors is correlated with the equity premium.  As we argue
earlier, this result does not imply that the model will forecast well,
which we look at next.

@@

Figures~\ref{fig:empirics1} plots the \ols\ results and
Figure~\ref{fig:empirics2} imposes
\citepos{campbell-thompson-2008-rfs} restriction.  The solid line
in each figure shows the \oos\ average, $\bar D_1$, and the shaded
region indicates the 95\% one-sided confidence interval implied by the
\dmw\ test.  Negative numbers indicate that the kitchen sink model has
higher out-of-sample loss.  We can see that the same patterns hold for
both models: the performance difference decreases with $R$, but the
kitchen sink model is never more accurate.  We also see that the
performance difference decreases suddenly over the period $R=29$ to
$R=34$ (corresponding to the years 1956--1961).
Figure~\ref{fig:empirics3} plots the accuracy of the individual
forecasts (only for the linear models) and shows that this change is
the result of a sudden improvement in the kitchen sink model.  This
change may indicate instability in the underlying relationship, as
\citet{goyal-welch-2008-rfs} propose.

In summary, we fail to reject the null that the benchmark prevailing
mean model is more accurate than \citepos{goyal-welch-2008-rfs}
kitchen sink.  This result is consistent with Goyal and Welch's
original analysis.  Unlike Goyal and Welch, we attribute this result,
at least in part, to parameter uncertainty---the full sample results
indicate that the larger model could predict better than the
benchmark with enough data.  Obviously, this is an illustrative
exercise only and is not meant to be comprehensive.  In this dataset,
there is likely parameter instability that we have not addressed, and
we have not dealt with variable persistence at all.
\section{Conclusion}\label{sec:conclusion}
This paper gives a theoretical motivation for using \oos\ comparisons:
the \dmw\ \oos\ test allows a forecaster to conduct inference about
the expected future accuracy of his or her models when one or both is
overfit.  We show analytically and through Monte Carlo that existing
in-sample test statistics can not test hypotheses about this
performance.

Our paper also shows that popular test and training sample sizes may
give misleading results if researchers are concerned about
overfit.\footnote{As we mention in the introduction, forecasters also
  use these statistics if they are concerned about unmodeled
  instability, which this paper does not address.}  We show that
$P^2/T$ must converge to zero for the \dmw\ test to give valid
inference about the expected forecast accuracy, otherwise the test
measures the accuracy of the estimates constructed using only the
training sample.  In empirical research, $P$ is typically much larger
than this.  Our simulations indicate that using large values of $P$
with the \dmw\ test gives undersized tests with low power, so this
practice may favor simple benchmark models too much.  Existing
corrections, proposed by
\citet{clark_tests_2001,clark_evaluating_2005},
\citet{mccracken_asymptotics_2007} and
\citet{clark_using_2006,clark_approximately_2007}, seem to correct too
much, though, and reject too often when the benchmark model is more
accurate.

@@

The proof is virtually identical to the proof of Proposition 2.3 in
\citet{merlevede_coupling_2002} and is omitted.

@@

\begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 2.]
  A modification of \citepos{de_jong_central_1997} \clt s for
  mixingale and \ned\ arrays will complete the proof.

>>>>

\frenchspacing \title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Michael McCracken, Seth Pruitt, Ross
    Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010 Joint
    Statistical Meetings, and in many seminars at \textsc{ucsd}, and
    espeically Graham Elliott for their valuable suggestions, feedback
    and advice in writing this paper.  I would also like to thank Amit
    Goyal for providing computer code and data for his 2008 RFS paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University,
  Economics Department}
\date{October 24, 2011}

@@

Although \oos\ comparisons have been popular in macroeconomics and
finance since \citepos{MeR:83} seminal study of exchange rate models,
it is unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using \oos\ comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the F-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular \oos\ test statistics under conditions
that would justify these full-sample tests.\footnote{In this paper, we
  will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
of the subsequent research by \citet{CCS:01}, \citet{ClM:01,ClM:05},
\citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07}, \citet{Mcc:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons.\footnote{Like us,
  \citet{Ana:07} allows the number of regressors to increase with $T$.
  But in that paper, they increase slowly enough that the \ols\
  coefficients are consistent and asymptotically normal.}
\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
focusing on hypotheses that can be tested by in-sample comparisons,
\citet{GiW:06} derive an \oos\ test for the null hypothesis that the
difference between two models' \oos\ forecasting performance is
unpredictable, a martingale difference sequence, \citet{GiR:09} test
whether the \oos\ forecasting performance of a model suffers from a
breakdown relative to its in-sample performance, and \citet{GiR:10}
test whether the forecasting performance is stable. However, those
papers focus on a particular \oos\ estimation strategy and do not
address why naive \oos\ comparisons might be generally useful.

Since in-sample and \oos\ statistics require similar assumptions and
test similar hypotheses, one might expect that they would give similar
results.  They do not.  Generally in-sample analysis supports more
complicated theoretical models and \oos\ analysis supports simple
benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
\citet{GoW:08}.  Since these different approaches strongly influence
the outcome of research, it is important to know when each is
appropriate.  The explanations in favor of \oos\ comparisons claim
that they should be more robust to unmodeled instability
\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
comparison is invalid and the \oos\ comparisons are more reliable.  Of
course, as \citet{InK:04,InK:06} point out, both in-sample and \oos\
methods could be valid, but the \oos\ methods could have lower power.

In this paper, we study the ``overfit'' possibility and leave
``instability'' to future research. This paper uses dimension
asymptotics to study the behavior of \oos\ comparisons when at least
one of the models is overfit---when the number of its regressors
increases with the number of observations so that their ratio remains
positive.  We focus on linear regression models estimated with a fixed
training window, but our basic conclusions should be true for other
estimation strategies and models as well.  Under this asymptotic
theory, the \ols\ coefficient estimator is no longer consistent or
asymptotically normal \citep{Hub:73} and has positive variance in the
limit.  Even so, we show that the usual \oos\ average is
asymptotically normal and can consistently estimate the difference
between the models' expected loss in periods $T+1,T+2,\dots$
conditional on the on the data available in period $T$, a time-series
analogue to the generalization error.\footnote{See, for example,
  \citet{HTF:08}.}  Under these asymptotics, the generalization error
does not converge to the expected performance of the pseudo-true
models, so the in-sample and \oos\ comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our theory,
the model that is closer to the true \dgp\ in population can forecast
worse.  In such a situation, an in-sample comparison would correctly
reject the null hypothesis that the benchmark is true, and an \oos\
comparison would correctly fail to reject the null that the benchmark
is more accurate.\footnote{In a pair of papers similar to ours,
  \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that the
  larger model has nonzero coefficients that are too close to zero to
  expect the model to forecast more accurately.  Like this paper, they
  argue that the larger model can be true but less accurate.  However,
  they focus on an aspect of the \dgp\ that makes this phenomenon
  likely, while we focus on the coefficient estimates that produce
  less accurate forecasts.}

This result justifies \oos\ comparisons when researchers want to
choose a model for forecasting.  Although there has been little
emphasis on hypothesis testing in this setting, testing is usually
appropriate: there is usually a familiar benchmark model in place, and
the cost of incorrectly abandoning the benchmark for a less accurate
alternative model is higher than the cost of incorrectly failing to
switch to a more accurate alternative.\footnote{These costs can be
  monetary, in the form of computer upgrades, software installation,
  and training, or they can be reputational costs.}
We show that the \dmw\ test lets the forecaster control the
probability of the first error, just as with conventional hypothesis
testing.

@@

Since the \ols\ coefficient estimator is no longer consistent or
asymptotically normal, the F-test and Wald tests are no longer
asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
naive comparisons of in-sample loss overestimate models' accuracy by a
factor proportional to $K/T$, $K$ being the number of regressors.  But
modifications of the F-test are valid under this asymptotic theory, as
shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
\citet{Cal:10}, among others.  Such results establish that hypotheses
about the parameters of the \dgp\ can be tested in-sample even if one
or both models are overfit.  For that very reason, these tests can not
reliably choose a model for forecasting and will reject the benchmark
too often.  We show this analytically in Section~\ref{sec:insample}.
Moreover, under this asymptotic theory, many recent \oos\ test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
F-test.  These tests are also designed to reject the benchmark when
the alternative model is true, and so they may reject too often when
the benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
\infty$ (with the number of regressors fixed), these statistics behave
like the \dmw\ test when $P$ is small, but should over-reject the
benchmark when $P$ is large.  Section~\ref{sec:mc} presents
simulations that support these claims.

@@

The first assumption is a standard condition on the dependence of the
underlying stochastic array.  We assume that the array is absolutely
regular instead of strong mixing, which is more common in
econometrics, because absolute regularity admits a particular coupling
argument \citep{Ber:79} that is unavailable for strong mixing
sequences.  Please see, for example, \citet{Dav:94} for a discussion
of these mixing conditions.

@@

The next assumption restricts the class of variance estimators we will
consider.  We use the same class of estimators studied by
\citet{DeD:00} (their class $\mathcal{K}$); see
their paper for further discussion.

@@

Both sets of simulations support our theoretical results.  The first
simulation confirms that the \dmw\ \oos\ $t$-test is centered at $E_R
\bar D_1$ for all choices of $P$ and $R$ and is centered on $E_T \bar
D_2$ only when $P$ is small.  The second simulation confirms that the
\dmw\ test has correct size for the null hypothesis that $E_T \bar D_2
\leq 0$ when $P$ is small and that tests designed to test whether the
benchmark is true, like the F-test and Clark and West's (2006, 2007)
and McCracken's (2007) \oos\ tests can reject by much more than their
nominal size when testing the null $E_T \bar D_2 \leq 0$.
Moreover, these simulations demonstrate that the restriction $P^2/T
\to 0$ is binding in practice, as the \dmw\ test under-rejects and has
very low power when it is not satisfied.
\section{Empirical Exercise}\label{sec:empirics}
This section presents an analysis of equity premium predictability
similar to \citet{GoW:08}.\footnote{All of the calculations in this
  section are done in R \citep{Rde:10}.  We also use code provided by
  \citet{Zeh:02}, \citet{Zei:04}, and \citet{Har:10}.}  We estimate
the expected forecasting performance of the largest model they
consider, a model with 13 regressors, using 81 observations (annual
data from 1928 to 2009).  We construct confidence intervals for the
difference in performance between this model and a prevailing mean
benchmark, and do so for different values of $R$ and $P$ to examine
the effect of the training and test sample choice on this \oos\
statistic.  We find that the estimate of the larger model's \mse\
decreases relative to the benchmark as $R$ increases, but it is never
smaller than the benchmark's.  This result, combined with the larger
model's in-sample significance, suggests that there may be a real
relationship between the equity premium and some of these predictors,
but that the relationship can not be estimated accurately enough to be
useful for forecasting and supports \citepos{GoW:08}
conclusions.  These results hold even when imposing
\citepos{CaT:08} restriction that the equity
premium forecast be non-negative.

We'll start with a very brief review.  \citet{GoW:08}
study the \oos\ forecasting performance of different variables thought
to predict the equity premium (calculated as the difference between
the return on the S\&P 500 index and the T-bill rate).  Some of these
variables are listed in
Table~\ref{tab:equity}.\footnote{Table~\ref{tab:equity} only lists the
  variables used in \citepos{GoW:08} ``kitchen sink''
  model.  Some of the variables that they use in bivariate models are
  excluded from this model either because the series are too short or
  because the variables are linear combinations of other variables.}
\citet{GoW:08} estimate the \oos\ forecasting
performance of bivariate models of the form
\[
r_{t+1} = \beta_0 + \beta_1 x_t + \varepsilon_{t+1}
\]
using \ols\ with a recursive window, where $r_{t+1}$ is the equity
premium and $x_t$ is a generic predictor, as well as some larger
models.  They find that these models forecast no better than the
prevailing mean of the equity premium.
\citet{CaT:08} find that nonlinear extensions of
Goyal and Welch's models are more accurate, either imposing sign
restrictions on the estimated coefficients or imposing that the
forecast be non-negative, but do not test for significance.

Obviously, \citepos{GoW:08} bivariate models do not
match the asymptotic theory of this paper, so we restrict our
attention here to their ``kitchen sink'' model, which includes all of
the variables, except for a few dropped because of data availability or
(perfect) multicollinearity.  Formally, the benchmark and alternative models are
\begin{eqnarray}
  \label{eq:3}
  r_{t+1} &=& \mu + \varepsilon_{1,t+1} \\
  \label{eq:2}
r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \varepsilon_{2,t+1}  
\end{eqnarray}
respectively and are estimated by \ols\ using the fixed-window scheme.
The predictors are listed in Table~\ref{tab:equity}; for a detailed
description of each predictor, please see Goyal and Welch's original
paper.  In this model, there are 13 regressors (including the constant
term) and we estimate the coefficients using annual data from 1928 to
2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
present results for one of \citepos{CaT:08}
restricted forecasting models.  For this model, we estimate
\eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
non-negative for each forecast.  We then calculate the \oos\ test just
as for the unconstrained model.

Table~\ref{tab:gwinsample} gives the results of the full sample
regression for Equation~\eqref{eq:2}, using Newey-West standard errors
with two lags \citep{NeW:87}.\footnote{We compare the test statistic
  to critical values from the $F$-distribution.}  The $p$-value is
very small (less than 0.01), indicating that the coefficients are
nonzero in population and at least one of these predictors is
correlated with the equity premium.  As we argue earlier, this result
does not imply that the model will forecast well, which we look at
next.

@@

Figures~\ref{fig:empirics1} plots the \ols\ results and
Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction.  The
solid line in each figure shows the \oos\ average, $\bar D_1$, and the
shaded region indicates the 95\% one-sided confidence interval implied
by the \dmw\ test.  Negative numbers indicate that the kitchen sink
model has higher out-of-sample loss.  We can see that the same
patterns hold for both models: the performance difference decreases
with $R$, but the kitchen sink model is never more accurate.  We also
see that the performance difference decreases suddenly over the period
$R=29$ to $R=34$ (corresponding to the years 1956--1961).
Figure~\ref{fig:empirics3} plots the accuracy of the individual
forecasts (only for the linear models) and shows that this change is
the result of a sudden improvement in the kitchen sink model.  This
change may indicate instability in the underlying relationship, as
\citet{GoW:08} propose.

In summary, we fail to reject the null that the benchmark prevailing
mean model is more accurate than \citepos{GoW:08} kitchen sink.  This
result is consistent with Goyal and Welch's original analysis.  Unlike
Goyal and Welch, we attribute this result, at least in part, to
parameter uncertainty---the full sample results indicate that the
larger model could predict better than the benchmark with enough data.
Obviously, this is an illustrative exercise only and is not meant to
be comprehensive.  In this dataset, there is likely parameter
instability that we have not addressed, and we have not dealt with
variable persistence at all.
\section{Conclusion}\label{sec:conclusion}
This paper gives a theoretical motivation for using \oos\ comparisons:
the \dmw\ \oos\ test allows a forecaster to conduct inference about
the expected future accuracy of his or her models when one or both is
overfit.  We show analytically and through Monte Carlo that existing
in-sample test statistics can not test hypotheses about this
performance.

Our paper also shows that popular test and training sample sizes may
give misleading results if researchers are concerned about
overfit.\footnote{As we mention in the introduction, forecasters also
  use these statistics if they are concerned about unmodeled
  instability, which this paper does not address.}  We show that
$P^2/T$ must converge to zero for the \dmw\ test to give valid
inference about the expected forecast accuracy, otherwise the test
measures the accuracy of the estimates constructed using only the
training sample.  In empirical research, $P$ is typically much larger
than this.  Our simulations indicate that using large values of $P$
with the \dmw\ test gives undersized tests with low power, so this
practice may favor simple benchmark models too much.  Existing
corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
too often when the benchmark model is more accurate.

@@

The proof is virtually identical to the proof of Proposition 2.3 in
\citet{MeP:02} and is omitted.

@@

\begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 2.]
  A modification of \citepos{Dej:97} \clt s for
  mixingale and \ned\ arrays will complete the proof.

Define
\[\label{eq:z1}
  Z_i = \ZDef
\]
where $b_T$ is a sequence that satisfies $b_T\leq P$,
$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
\citepos{Dej:97} Theorem 1 show that
\begin{equation*}
   \SumOuterBlock{i} Z_i = \frac1{\sqrt{P}} \oosSum{s}{1} (D_{tR} - \E_R D_{tR}) + o_p(1).
\end{equation*}
and
\begin{equation*}
  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
  Z_i) + o_p(1).
\end{equation*}
Note that $\{Z_i - E_{R + (i-1)b_T},\mathcal{F}_{R + i b_T}\}_i$ is an
\mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
3.1 ensure that\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
  all $t \geq R$, so Hall and Heyde's condition (3.21) is
  unnecessary---see the remarks after their result.}
\[
\frac1{\sigma} \SumOuterBlock{i} Z_i \to^p
N(0,1)
\]
as long as
\begin{equation}\label{eq:cltvar2}
  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
\end{equation}
and
\begin{equation}\label{eq:cltvar1}
  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.
\end{equation}
Equation (\ref{eq:cltvar2}) holds as in \citet{Dej:97} (see the proof
of his Theorem 2); to see that (\ref{eq:cltvar1}) holds, we'll use an
argument based on his Lemma 5.  Define
\[
\tilde Z_i = \frac1{\sqrt{P}} \SumInnerBlock{s}{i} \tilde D_s -
\E_R \tilde D_s,
\]
with $\tilde D_{R+(i-1)b_T + 1},\dots,\tilde D_{R+ib_T}$ new random
variables that satisfy
\[
\lVert \tilde D_s - D_{sR} \rVert_2 \leq 2^{1 + \frac1\rho} B_L \beta_{s -
  (i-1)b_T + R}^{\rhoExp}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
\]
and
\[
\E_R \phi(\tilde D_s) = \E_{R+(i-1)b_T} \phi(\tilde D_s) \quad \text{a.s.}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
\]
for all measurable $\phi$ such that the expectations are finite; the
existence of these variables is ensured by Lemma
\ref{lem-basic-coupling}.  Then $\tilde Z_i$ satisfies
\[
\E_R \tilde Z_i^2 = \CEOuterBlock{\tilde Z_i^2}{i} \quad \text{a.s.},
\]
giving the inequality
\[
\lVert \ZSqCE - \E_R Z_i^2 \rVert_1 \wall= \lVert \wall\CEOuterBlock{(Z_i^2 -
  \tilde Z_i^2)}{i} \\ - (\E_R Z_i^2 - \CEOuterBlock{\tilde Z_i^2}{i})
\rVert_1 \return\\
\leq 2 \lVert Z_i^2 - \tilde Z_i^2 \rVert_1.
\return
\]
